### 2017-05-11 prince/samples/CalculusMadeEasyChapXV.tex

%2multibyte Version: 5.50.0.2960 CodePage: 1252
\documentclass[12pt,openany]{book}%
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{geometry}%
\setcounter{MaxMatrixCols}{30}
%TCIDATA{OutputFilter=latex2.dll}
%TCIDATA{Version=5.50.0.2960}
%TCIDATA{Codepage=1252}
%TCIDATA{LastRevised=Wednesday, August 10, 2016 12:02:22}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=Manual}
%BeginMSIPreambleData
\providecommand{\U}[1]{\protect\rule{.1in}{.1in}}
%EndMSIPreambleData
\def\tb{\begin{center}\rule{1.5in}{0.5pt}\end{center}}
\renewcommand{\thechapter}{\Roman{chapter}}
\setcounter{chapter}{14}
\geometry{margin=1in}
\begin{document}
%
%TCIMACRO{\TeXButton{B titlepage}{\begin{titlepage}}}%
%BeginExpansion
\begin{titlepage}%
%EndExpansion

@@

{\large 1914}
\end{center}%

@@

%TCIMACRO{\FRAME{dtbpF}{2.7233in}{2.5278in}{0pt}{}{}{calculusmadeeasyfig43.jpg}%
%{\special{ language "Scientific Word";  type "GRAPHIC";
%maintain-aspect-ratio TRUE;  display "USEDEF";  valid_file "F";
%width 2.7233in;  height 2.5278in;  depth 0pt;  original-width 2.6809in;
%original-height 2.4863in;  cropleft "0";  croptop "1";  cropright "1";
%cropbottom "0";
%filename 'CalculusMadeEasyFig43.jpg';file-properties "XNPEU";}}}%
%BeginExpansion
\begin{center}
\includegraphics[
natheight=2.486300in,
natwidth=2.680900in,
height=2.5278in,
width=2.7233in
]%
{CalculusMadeEasyFig43.jpg}%
\end{center}
%EndExpansion

What we have to investigate is the value of $\dfrac{d(\sin\theta)}{d \theta}$;
or, in other words, if the angle~$\theta$ varies, we have to find the relation
between the increment of the sine and the increment of the angle, both
increments being indefinitely small in themselves. Examine Fig 43, wherein, if
the radius of the circle is unity, the height of~$y$ is the sine, and $\theta$
is the angle. Now, if $\theta$ is supposed to increase by the addition to it
of the small angle $d \theta$---an element of angle---the height of~$y$, the
sine, will be increased by a small element~$dy$. The new height~$y + dy$ will
be the sine of the new angle $\theta+ d \theta$, or, stating it as an
equation,
\[
y+dy = \sin(\theta+ d \theta);
\]
and subtracting from this the first equation gives
\[
dy = \sin(\theta+ d \theta)- \sin\theta.
\]

@@

%TCIMACRO{\FRAME{dtbpF}{2.8202in}{2.2623in}{0pt}{}{}{project_gutenberg-1.bmp}%
%{\special{ language "Scientific Word";  type "GRAPHIC";
%maintain-aspect-ratio TRUE;  display "USEDEF";  valid_file "F";
%width 2.8202in;  height 2.2623in;  depth 0pt;  original-width 2.7778in;
%original-height 2.2226in;  cropleft "0";  croptop "1";  cropright "1";
%cropbottom "0";  filename 'project_gutenberg-1.bmp';file-properties "XNPEU";}%
%}}%
%BeginExpansion
\begin{center}
\includegraphics[
natheight=2.222600in,
natwidth=2.777800in,
height=2.2623in,
width=2.8202in
]%
{C:/George/Prince2/mozilla/prince/samples/CalculusMadeEasyChapXV__3.jpg}%
\end{center}
%EndExpansion
This sample document was derived from
\textit{\href{http://www.gutenberg.org/3/3/2/8/33283/}{\textit{Calculus Made
Easy, 2nd Edition} by Silvanus Thompson}}, from
\href{http://www.gutenberg.org/}{Project Gutenberg}. See the Project Gutenberg
licnesing information
\href{http://www.gutenberg.org/wiki/Gutenberg:The_Project_Gutenberg_License}{*here*}%
.

@@

\begin{enumerate}
\item .png, the logo on the first page

\item .jpg, Fig. 43

\item .wmf, Fig. 44

\item .eps, Fig 45

\item .bmp, the logo on the last page
\end{enumerate}

>>>>

%2multibyte Version: 5.50.0.2960 CodePage: 1252
\documentclass[12pt,openany]{book}%
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{geometry}%
\setcounter{MaxMatrixCols}{30}
%TCIDATA{OutputFilter=latex2.dll}
%TCIDATA{Version=5.50.0.2960}
%TCIDATA{Codepage=1252}
%TCIDATA{LastRevised=Wednesday, May 10, 2017 14:52:02}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=Manual}
%BeginMSIPreambleData
\providecommand{\U}[1]{\protect\rule{.1in}{.1in}}
%EndMSIPreambleData
\def\tb{\begin{center}\rule{1.5in}{0.5pt}\end{center}}
\renewcommand{\thechapter}{\Roman{chapter}}
\setcounter{chapter}{14}
\geometry{margin=1in}
\begin{document}
%
%TCIMACRO{\TeXButton{B titlepage}{\begin{titlepage}}}%
%BeginExpansion
\begin{titlepage}%
%EndExpansion

@@

{\large 1914}
\end{center}

%

@@

%TCIMACRO{\FRAME{fhF}{2.7233in}{2.5278in}{0pt}{}{}{calculusmadeeasyfig43.jpg}%
%{\special{ language "Scientific Word";  type "GRAPHIC";
%maintain-aspect-ratio TRUE;  display "USEDEF";  valid_file "F";
%width 2.7233in;  height 2.5278in;  depth 0pt;  original-width 2.6809in;
%original-height 2.4863in;  cropleft "0";  croptop "1";  cropright "1";
%cropbottom "0";
%filename 'CalculusMadeEasyFig43.jpg';file-properties "XNPEU";}} }%
%BeginExpansion
\begin{figure}[h]%
\centering
\includegraphics[
natheight=2.486300in,
natwidth=2.680900in,
height=2.5278in,
width=2.7233in
]%
{CalculusMadeEasyFig43.jpg}%
\end{figure}
%EndExpansion

What we have to investigate is the value of $\dfrac{d(\sin\theta)}{d\theta}$;
or, in other words, if the angle~$\theta$ varies, we have to find the relation
between the increment of the sine and the increment of the angle, both
increments being indefinitely small in themselves. Examine Fig 43, wherein, if
the radius of the circle is unity, the height of~$y$ is the sine, and $\theta$
is the angle. Now, if $\theta$ is supposed to increase by the addition to it
of the small angle $d\theta$---an element of angle---the height of~$y$, the
sine, will be increased by a small element~$dy$. The new height~$y+dy$ will be
the sine of the new angle $\theta+d\theta$, or, stating it as an equation,
\[
y+dy=\sin(\theta+d\theta);
\]
and subtracting from this the first equation gives
\[
dy=\sin(\theta+d\theta)-\sin\theta.
\]

@@

%TCIMACRO{\FRAME{dtbpFX}{2.8202in}{2.2623in}{0pt}{}{}{project_gutenberg-1.bmp}%
%{\special{ language "Scientific Word";  type "GRAPHIC";
%maintain-aspect-ratio TRUE;  display "USEDEF";  valid_file "F";
%width 2.8202in;  height 2.2623in;  depth 0pt;  original-width 2.7778in;
%original-height 2.2226in;  cropleft "0";  croptop "1";  cropright "1";
%cropbottom "0";  filename 'project_gutenberg-1.bmp';file-properties "XNPEU";}%
%}}%
%BeginExpansion
\begin{center}
\fbox{\includegraphics[
natheight=2.222600in,
natwidth=2.777800in,
height=2.2623in,
width=2.8202in
]%
{C:/George/Prince2/mozilla/prince/samples/CalculusMadeEasyChapXV__3.jpg}%
}
\end{center}
%EndExpansion
This sample document was derived from
\textit{\href{http://www.gutenberg.org/3/3/2/8/33283/}{\textit{Calculus Made
Easy, 2nd Edition} by Silvanus Thompson}}, from
\href{http://www.gutenberg.org/}{Project Gutenberg}. See the Project Gutenberg
licnesing information
\href{http://www.gutenberg.org/wiki/Gutenberg:The_Project_Gutenberg_License}{*here*}%
.

@@

\begin{enumerate}
\item .png, the logo on the first page using in line placement

\item .jpg, Fig. 43 using floating placement with only the here placement option

\item .wmf, Fig. 44 using displayed placement

\item .eps, Fig 45 using displayed placement

\item .bmp, the logo on the last page using displayed placement with a frame
around the graphic
\end{enumerate}
